---
title: "R Notebook"
output:
  pdf_document: default
  html_document: default
---

## Introduction

In this notebook, I will be analyzing the political contributions of UCSB professors.

## Data Reading and Preprocessing

```{r}
setwd('/Users/stellajia/Desktop/UCSB/Extracurriculars/Daily_Nexus/political_contributions/')
library("tidyverse")
library("lubridate")
data <- read.csv("ucsb_professors.csv")
```

```{r}
library("scales")
# test commit
```

```{r}
head(data, 5)
```

```{r}
# keep relevant columns
keep <- c("committee_id", "committee_name", "report_year", "contributor_name", "contribution_receipt_amount", "contribution_receipt_date")
df = data[keep]
head(df, 5)
```

```{r}
# remove time from string and convert from 'chr' to 'date' type
df$contribution_receipt_date <- as.Date((gsub(" 00:00:00", "", df$contribution_receipt_date)), "%Y-%m-%d")
df
```

### Column Information

-   committee_id: unique ID given to a political organization/committee
-   committee_name: name of political organization/committee
-   report_year: year that individual donated to a certain committee
-   contributor_name: name of contributor who donated
-   contribution_receipt_amount: amount of money the contributor donated to a certain committee

## Distribution of Donations

```{r}
# create new dataframe which groups all contributions made on SAME date 

df %>% 
  group_by(contribution_receipt_date) %>% 
  summarise(daily_contribution = sum(contribution_receipt_amount)) %>% 
  filter(daily_contribution > 0) %>% 
  ggplot(aes(x=contribution_receipt_date, y=daily_contribution)) +
    geom_bar(stat = "identity") + #tells ggplot that you're providing y values
    labs(x = "Month", y = "Amount Contributed") 
    #scale_x_date(labels = date_format("%m-%Y")) +
    #annotate(geom="text", x = parse_date_time("11/8/2016", "%m/%d/%Y %H:%M"), y = 5, label="2016 Presidential Election,", hjust=0.5)
```

```{r}
# create bigger bin widths so group by week?
df %>% 
  group_by(contribution_receipt_date) %>% 
  summarise(daily_contribution = sum(contribution_receipt_amount)) %>% 
  filter(daily_contribution > 0) %>% 
  
  mutate(week = cut.Date(contribution_receipt_date, breaks = "1 week", labels = FALSE)) %>% 
  # could be working with diff date objects after cut.Date
  arrange(contribution_receipt_date) %>% 
  group_by(week) %>% 
  summarise(weekly_contribution = sum(daily_contribution)) %>% 
  
  ggplot(aes(x=week, y=weekly_contribution)) +
    geom_bar(stat = "identity") + 
    labs(x = "Week", y = "Amount Contributed") 
    scale_x_time(
      breaks=parse_date_time(c("2015-1-1", "2021-8-15", "2021-9-1", "2021-9-15", "2021-12-15"), "%Y-%m-%d"),
      labels=c("Jan. 1, 2015", "Aug. 15", "Aug. 31", "Sept. 15", "Dec. 15, 2021")
    )
```

## Money Per Organization

```{r}
df %>% 
  group_by(committee_name) %>% 
  summarise(total_contribution = sum(contribution_receipt_amount)) %>% 
  arrange(desc(total_contribution)) %>% 
  top_n(10) %>% 
  
  ggplot(aes(x=committee_name, y=total_contribution)) +
    geom_bar(stat="identity") +
    labs(x = "Organization", y = "Total Contributed") +
    scale_x_discrete(label=abbreviate)
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# consider splitting by year
```
